### 2020-03-20 paper/main.tex
added information about classes

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/dataset_info.png}
   \end{center}
   \caption{Size of each dataset.}
   \label{fig:stft_example}
\end{figure}

@@

>>>>

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/dataset_info.png}
   \end{center}
   \caption{Size of each dataset.}
   \label{fig:dataset_info}
\end{figure}

@@

\section{Dataset Classes}

Dataset A and C were generated through similar methods and can be visually seen in Figure \ref{fig:dataset_ac}. There are three base stations, in which each base station corresponds to a class, sending information to a single receiver antenna.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.4]{../media/dataset_ac.png}
   \end{center}
   \caption{Class representation of how dataset A and C.}
   \label{fig:dataset_ac}
\end{figure}

Dataset B differs from dataset A and C in how it transmits data. In \ref{fig:dataset_b}, we can see that there are three different antennas at the same station sending information to a single receiver station. The problem of classification becomes more challenging because they are very close together.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/dataset_b.png}
   \end{center}
   \caption{Class representation of how dataset B.}
   \label{fig:dataset_b}
\end{figure}
